Improving cropland maps through tight integration of human and machine intelligence

### 2020-07-31 inst/manuscript/manuscript.Rmd
Extracted and processed fields and segements from validation sites.

```{r, echo = FALSE, out.width="80%", fig.cap="The overall, user's, and producer's accuracies (indicated by fill color) for each of the 16 mapping zones (zones numbers are shown on maps) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/figure5.png')
```

@@

###

>>>>

```{r, echo = FALSE, out.width="80%", fig.cap="The overall, user's, and producer's accuracies (indicated by fill color) for each of the 16 mapping zones (zones numbers are shown on maps) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/si_mapping_blocks.png')
```

@@

### Segmentation accuracy
To evaluate the accuracy of the segmented field boundaries, we calculate the mean and standard deviation of the most accurate (for the given AOI) labeller's maps for validation sites, calculated the mean and standard deviation of area, and compared these statistics to those derived from the model-generated segments for those sites (Figure X).
